---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# imputeangles

<!-- badges: start -->
<!-- badges: end -->

The goal of imputeangles is to provide imputation methods for incomplete angular data for use with the `mice` package.

## Installation

You can install the development version of imputeangles from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("benjamin-stockton/imputeangles")
```

## Example

As an example of stand-alone use (i.e. without the `mice` package), we construct a simulated data set with missing angles and impute the missing angles with projected normal regression.

```{r}
library(imputeangles)

N <- 100
x <- rnorm(N)
B <- matrix(c(3.5, 1, -3, 0), nrow = 2, byrow = TRUE)
y <- bpnreg_draw(x, B)
mis <- sample(N, size = floor(0.5 * N), replace = FALSE)
y[mis] <- NA
ry <- !is.na(y)

mice.impute.bpnreg(y, ry, x)
```

For use with `mice`, the package should be loaded and the functions called as follows:

``` r
library(mice)
library(imputeangles)

N <- 100
x <- rnorm(N)
B <- matrix(c(3.5, 1, -3, 0), nrow = 2, byrow = TRUE)
y <- bpnreg_draw(x, B)
mis <- sample(N, size = floor(0.5 * N), replace = FALSE)
y[mis] <- NA
dat <- data.frame("theta" = y, 
                  "X" = x)
                  
imps <- mice(dat, method = c("bpnreg", "norm"), m = 5)
```
